%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Udit}{Desai}{
  1497, Fruitdale Avenue, San Jose, CA - 95128 \\
  \href{mailto:desaiuditd@gmail.com}{desaiuditd@gmail.com} | 831.212.4307
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Santa Clara University}
\descript{MS in Computer Science}
\location{Expected June 2017 | Santa Clara, CA \\ GPA: 3.22}
\sectionsep

\subsection{DA-IICT}
\descript{MS in Information Technology}
\location{May 2013 | Gandhinagar, India \\ GPA: 3.13}
\sectionsep

\subsection{University of Pune}
\descript{BS in Computer Science}
\location{June 2011|  Pune, India \\ GPA: 3.17}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/desaiuditd}{\custombold{desaiuditd}} \\
LinkedIn://  \href{https://www.linkedin.com/in/desaiuditd}{\custombold{desaiuditd}} \\
Devpost://  \href{https://devpost.com/desaiuditd}{\custombold{desaiuditd}} \\
Blog://  \href{http://blog.incognitech.in}{\custombold{Incognitech}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Pattern Recognition \& Data Mining \\
Web Search Information Retrieval \\
Big Data \\
Distributed Computing \\
Web Infrastructure \& IoT \\
Software Ethics \\
Software Management \\
\sectionsep

\subsection{Undergraduate}
Computer Architecture \\
Operating Systems \\
Compiler Construction \\
Microcontrollers \& Microprocessors \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
JavaScript \textbullet{} Java \textbullet{} PHP \textbullet{} Ruby \textbullet{} ShellScript \textbullet{} EcmaScript \textbullet{} R \textbullet{} Python \\~\\
\subsection{Frameworks}
Node \textbullet{} Meteor \textbullet{} Express \textbullet{} Android \textbullet{} WordPress \textbullet{} Backbone \textbullet{} Ruby on Rails \textbullet{} ElasticSearch \textbullet{} React \\~\\
\subsection{Database}
SQL \textbullet{} MongoDB
%\location{Over 5000 lines:}
%\location{Over 1000 lines:}
%\location{Familiar:}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Santa Clara University}
\descript{| Research Assistant }
\location{January 2016 – January 2017 | Santa Clara, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led a team for a cross-platform application called HOME for \textbf{Community Technology Alliance} who is a partner of \textbf{Frugal Innovation Lab} incubated within Santa Clara University.
\item Successfully delivered the first phase of HOME app with VI-SPDAT scoring algorithm, HMIS data integration and a survey management module using Meteor – a Node.js cross platform framework.
\end{tightemize}
\sectionsep

\runsubsection{Community Technology Alliance}
\descript{| Software Engineer Intern }
\location{January 2016 – January 2017 | Santa Clara, CA}
\begin{tightemize}
\item Led a cross-platform software project called HOME with VI-SPDAT algorithm, HMIS data integration and a survey management module using Meteor – a Node.js cross platform framework.
\item Working on Data Analytics tools like Tableau, Looker to process and analyse data for homeless people.
\end{tightemize}
\sectionsep

\runsubsection{Google}
\descript{| Software Engineering Intern }
\location{May 2013 – Aug 2013 | Mountain View, CA}
\begin{tightemize}
\item Worked on the YouTube Captions team in primarily vanilla Javascript and Python to plan, design and develop the full stack implementation of a new framework to add and edit Automatic Speech Recognition captions.
\item Created a backbone.js-like framework for the Captions editor.
\item All code was reviewed, perfected, and pushed to production.
\end{tightemize}
\sectionsep

\runsubsection{Phabricator}
\descript{| Open Source Contributor \& Team Leader}
\location{Jan 2013 – May 2013 | Palo Alto, CA \& Ithaca, NY}
\begin{tightemize}
\item Phabricator is used daily by Facebook, Dropbox, Quora, Asana and more.
\item I created the Meme generator, the entire Lipsum application, ported Tokens to different apps, fixed many bugs and more in PHP and Shell.
\item Led a team from MIT, Cornell, IC London and UHelsinki for the project.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Cornell Robot Learning Lab}
\descript{| Head Undergrad Research}
\location{Jan 2014 – Present | Ithaca, NY}
Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  Publication submitted.
\sectionsep

\runsubsection{Cornell Phonetics Lab}
\descript{| Head Undergraduate Researcher}
\location{Mar 2012 – May 2013 | Ithaca, NY}
Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2014	     & top 52/2500  & KPCB Engineering Fellow\\
2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
2013	     & National  & Jump Trading Challenge Finalist\\
2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
2010     & National & Comp. Soc. of India's National Programming Contest\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

\begin{tabular}{rll}
2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
2014   & National   & The Global Leadership and Education Forum (tGELF)\\
2012   &  National  & Golden Key International Honor Society\\
2012   &  National   & National Society of Collegiate Scholars\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}