%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}

\color{primary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Udit}{Desai}{
  Unit 33, 29-33, Joyce Street, Pendle Hill, NSW - 2145 \\
  \href{tel:+61459343918}{+61.459.343.918} |
  \href{mailto:desaiuditd@gmail.com}{desaiuditd@gmail.com} |
  \href{https://blog.incognitech.in}{https://blog.incognitech.in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\subsection{Santa Clara University}
\descript{MS in Computer Science}
\location{June 2017 | Santa Clara, CA}
\sectionsep
\sectionsep

\subsection{DA-IICT}
\descript{MS in Information Technology}
\location{May 2013 | Gandhinagar, India}
\sectionsep
\sectionsep

\subsection{University of Pune}
\descript{BS in Computer Science}
\location{June 2011 | Pune, India}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
\begin{tabular}{ l l }
Github: & \href{https://github.com/desaiuditd}{@desaiuditd} \\
LinkedIn: & \href{https://www.linkedin.com/in/desaiuditd}{@desaiuditd} \\
Devpost: & \href{https://devpost.com/desaiuditd}{@desaiuditd}
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
TypeScript \textbullet{} JavaScript \textbullet{} PHP \textbullet{} Go \\
ShellScript \textbullet{} Ruby \textbullet{} R \textbullet{} Python
\sectionsep
\sectionsep

\subsection{Frameworks}
NodeJS \textbullet{} Express \textbullet{} React \textbullet{} Gutenberg \\
WordPress \textbullet{} BackboneJS \textbullet{} Kafka \\
MeteorJS \textbullet{} Ruby on Rails \textbullet{} ElasticSearch
\sectionsep
\sectionsep

\subsection{Database}
MySQL \textbullet{} PostgreSQL \textbullet{} MongoDB
\sectionsep
\sectionsep

\subsection{Tools}
Git \textbullet{} Subversion \textbullet{} Jira \textbullet{} AWS \\
Jekyll \textbullet{} Amazon Alexa \textbullet{} IBM Watson
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Coursework}
%\subsection{Graduate}
%Pattern Recognition \& Data Mining \\
%Web Search Information Retrieval \\
%Big Data \\
%Distributed Computing \\
%Web Infrastructure \& IoT \\
%Software Ethics \\
%Software Management \\
%\sectionsep

%\subsection{Undergraduate}
%Computer Architecture \\
%Operating Systems \\
%Compiler Construction \\
%Microcontrollers \& Microprocessors \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
%\sectionsep

\section{Extra Curriculum}

\subsection{Open Source}
\location{March 2014 – Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Contributions in \href{https://github.com/WordPress/gutenberg/pulls?q=is\%3Apr+author\%3Adesaiuditd}{Gutenberg}
\item \href{https://core.trac.wordpress.org/report/25?USER=desaiuditd}{Contributions} in \href{https://github.com/WordPress/wordpress-develop/pulls?q=is\%3Apr+author\%3Adesaiuditd}{WordPress Core}
\item Other \href{https://profiles.wordpress.org/desaiuditd/#content-plugins}{WordPress Plugins}
\end{tightemize}
\sectionsep


\subsection{Freelance}
\location{WordPress Development | Remote}
\location{February 2014 – August 2015}
\begin{tightemize}
\item \textbf{\textit{WordPress Engineer}} at XWP.co Pty. Ltd., Australia
% \item Built Widget Tracking module for Stream WordPress plugin
% \item Developed XWP’s new website for 2014.
\end{tightemize}
\location{December 2014 – August 2015}
\begin{tightemize}
\item \textbf{\textit{Lead Engineer}} at Moxie Media Group, USA
% \item Built up software requirements \& developed websites for clients.
\end{tightemize}
\location{June 2022 – September 2023}
\begin{tightemize}
\item \textbf{\textit{Web Engineer}} at 10up, EMEA (UK)
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Nine Publishing}
\descript{| Senior Software Engineer }
\location{April 2018 – Present | Sydney, Australia}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Empowering the newsrooms behind Sydney Morning Herald, The Age, Brisbane Times \& Australian Financial Review by building world class editorial tools and publishing platform.
\end{tightemize}
\sectionsep

\runsubsection{OpenMessage}
\descript{| Full Stack Engineer }
\location{August 2017 – February 2018 | San Francisco, CA, USA}
\begin{tightemize}
\item Designed architecture and implemented OpenMessage backend API to send multimedia messages using NodeJS and OpenAPI specification.
\item Built front-end application to interact with the backend API using React.
\end{tightemize}
\sectionsep

\runsubsection{Santa Clara University}
\descript{| Research Assistant }
\location{January 2016 – January 2017 | Santa Clara, CA, USA}
\begin{tightemize}
\item Developed, deployed and launched HOME application v1.0 for Monterey City council.
\item Integrated HOME app with HMIS hadoop cluster by implementing OAuth 2.0 strategy.
\item Collected data for 10,000+ homeless people and verified them for housing by implementing VI-SPDAT scoring algorithm.
\item Resolved 300+ issues and reduced testing time with 70\% by implementing automated unit test framework using TravisCI \& Mocha.
\end{tightemize}
\sectionsep

\runsubsection{rtCamp}
\descript{| Web Developer }
\location{May 2013 – February 2015 | Pune, India}
\begin{tightemize}
\item Increased revenues for clients with 20\% by developing 10 websites from scratch \& developing WordPress themes \& plugins.
\item Increased rtCamp’s CRM performance with 25\% by leading the development team for rtBiz - CRM tool.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Ink Authoring}
\location{}
\begin{tightemize}
\item Ink Authoring is a publishing tool built on top of WordPress and its new block based editor Gutenberg. It helps our newsrooms of SMH, The Age \& AFR to write news articles and publish them on our news websites and mobile apps.
\end{tightemize}
\sectionsep

\runsubsection{SlyCam}
\location{}
\begin{tightemize}
\item Notified who visited your house and opened door remotely by building an IoT door lock system using Node.js, MongoDB, AWS, Adruino, Motion Sensor, Camera module \& ESP8266.
\end{tightemize}
\sectionsep

\runsubsection{Wayfarer}
\location{}
\begin{tightemize}
\item Wayfarer is a machine learning based recommendation system for your travel plans. It helps you by performing a layered Sentiment Analysis on your Twitter profile using Python \& R for Data crunching, React Native, IBM Watson API \& Amazon Alexa.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hackathons} 
\begin{tabular}{ l l l l }

Apr, 2017 & BroncoHack & Best use of AWS & \href{https://github.com/desaiuditd/slycam}{Github} \\

Jan, 2017 & HackUCSC & Best use of Microsoft Azure & \href{https://github.com/desaiuditd/outtatheblues}{Github} \\

Nov, 2016 & HackRice & Top 6 Finalists  & \href{https://github.com/desaiuditd/wayfarer}{Github} \\

Sep, 2016 & TechCrunch Disrupt & Best WordPress Data Hack & \href{https://github.com/desaiuditd/incognitech}{Github} \\

Jun, 2016 & HackDavis & Best User Voice Experience & \href{https://github.com/desaiuditd/roomscore}{Github} \\

\end{tabular}

\end{minipage} 
\end{document}
\documentclass[]{article}
